Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-11 prop_letter.tex
prop_letter.tex \section{Born} Updating...

Since $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, every function~$\iota_{1}\circ\mu$
on a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
Hilbert space, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
is not a QIVPM. This highlights the necessity to have conditions disregarding
the dimension of the Hilbert space.

@@

Since $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not
a QIVPM, we know $\iota_{1}$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
and the right-end~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
$\iotal$ must be continuous on the unit open interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
which implies the number of intervals that $\iota$ maps to must be
uncountable.

\begin{thm}If $\iota$ satisfies the Statements in Thm.~\ref{thm:iota-statements},
then the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
or contains uncountably many intervals.\end{thm}

>>>>

On the one hand, $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies
Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}
so that every function~$\iota_{1}\circ\mu$ on a three-dimensional
Hilbert space is a QIVPM. On the other hand, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
is not a QIVPM on four-dimensional Hilbert space. Therefore, we need
to strengthen Eqs.~(\ref{eq:iota-constraints}) and Eq.~(\ref{eq:iota-add})
to guarantee $\iota\circ\mu$ is always a QIVPM.

@@

In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end function~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
and the right-end function~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
the left-end function~$\iotal$ must be continuous on the unit open
interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
which implies the number of intervals that $\iota$ maps to must be
uncountable.

\begin{thm}For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $
or $\mathscr{I}$ contains uncountably many intervals.\end{thm}
